Transforming Trash as an Artistic Act

### 2016-01-01 chapter4_reduced.tex
updates
Former-commit-id: ed8c3a549dfd42e9a1714a8835097ccd033fd632

@@

%
%
% TODO: Burada geçmiş, şimdiki zamanlara dikkat etmek gerek.
\section{The Statement}
% TODO Ekolojik, harmful, iğreç falan diye de değinmek gerekli bence.
% --disgusting, abject, unattractive, harmful to the people and nature--
Refuse is part of people’s consumption practices. It is a very common concept from developed cities to rural areas, from modern societies to ancient societies. It is not wanted, thrown away, kept away. It is considered as useless and disgusting. Contrary to the common approach as \cite{thompson1979rubbish}, author of the book Rubbish Theory, stated \quotes{one man's trash is another man's treasure}.

% Her zaman her yerde olan çöp.
% people are invited in the phase of collecting and finding trash
With the collaboration of many people discarded papers and packages were collected from different places. This time, it was not thrown away, it was collected and saved. Later they were transformed to notebooks by hand with traditional methods. Juxtaposition of trashes create notebooks that are different from the blank industrial ones, and through them challenged the widespread understanding of trash.

@@

% Bu proje çöpte yeni imkanlar bulmayı amaçlıyor. İnsanların tekrar onları hayatlarına sokmalarını istiyor.

@@

% Artist's work and their approach supported my project.
Through the process, there are several problems that needed to be solved. Some of the questions in my mind are solved through the research on trash. Further, the found samples of artworks helped me a lot to shape unclear points of the project. They provide me a deeper understanding of the subject and what I am doing. They lead me during the development of the work.
% played significant role.
% It is evolved in time and affected from other artists' work, and gain meaning from research.

% This progress also reveals the how this work can be positioned among the other works.

@@

% Temel fikir sonra kullanmak için saklamak gerektigi. Bu acidan bakildiginda song dongun annesinin pratigi ile benzerlik gostermektedir. Song durumunda etkili olan farktorler ekonomik zorluklar ve boslugun doldurulmasiyla ilgili iken buradaki tam olarak belli degil. Ama benim yaklasimi aciklayan bir sey. Daha sonra kullanmak icin saklamak.

% [EXPERIMENTS AT HOME]
Most remarkable interaction with trash is from recent years. Long years I stayed at dormitory during when I was high school and university while undergraduate. Dormitory is place that living spaces is shared with many people. Therefore there is a limited place for you and your possessions. There is no space for unused items. After I graduated from university I started to living a rented house. This give me to opportunity to save the materials to use them later. My very first intention is to use them on my painting. Instead of white blank canvas I want to experiment with different surfaces. I collected boxes and cart boards from my friends. My aim is to turn discard materials to the different things. Here is some of the my previous works.

@@

% Bu calismalardaki amacim farkli yuzeylerde resim yapabilmekti. Copu uzerine bir swyler yapmak benim icin yeni bir sey yapmakti. Deneysel bir yaklasimdi. Bir digeri ise bedavaydi. Kolayca elde edilen bir malzeme ve rahat ucuzlugundan dolayi bana daha fazla deneme imkani sunmaktaydi.

% cok ve kolay ulasilabildigi icin deneme imkani da cok. Benim icin cok iyi bir durum.

% Artik biriktirip, onlari daha sonrasi icin kullanabilirdim. Bunlari sadece yapmakla kalmiyordum, cevremdeki insanlara gosteriyordum, onlara hediye olarak veriyordum.

% ben bir suru bir suru yapiyordum. Kendi urunumu kendimin yapmak istiyordum.

% cope bakis acim buradan hissedilebilir.

% tum imkansizliklara ragmen copten bir sey yapmak yerine aslinda imkanlarla birlikte copten bir sey yapmak. Hazir bir sey kullandigim zaman kolay kacmak olarak goruluyor. Ama benim amacim zoru basarmak degil ki? Boyle bir zorlamaya gerek var mi emin degilim. Bu zorlamanin artisi nedir bilmiyorum.

% ben boyle kimsenin yapamayacagi bir seyle ugrasmak istemiyorum. Sadece ben yapmis olmak istemiyorum. Herkes yapabilir. Hatta yaapsin. Ben sadece yapan insani gostermek istiyorum.

@@

% But covering things are not new actually, when we are primary school again, we cover our books and notebooks. My mother, she is also a teacher, still covers her books things whatever at hand. (I have remembered that we are covering our notebooks at school. Sometimes we also cover the books.)

% bir yandan free olması experiment yapmak için ideal olması.

%\textbf{What do I think about trash?} I need to clarify my approach to the trash, wasting and discarding. First point is that I am very uncomfortable to the action of discarding thing. I always think that by discarding this think I am missing something rather than getting rid of something. Sometimes because of the significant amount of residue from consumption from daily activities I became overwhelmed and to move on I need to leave behind them and move on. However almost it is never ending loop. (I believe that sometimes we need to break the loops to realize different meanings. To think outside the box, we need to behave outside of common habits. As I mentioned the discarding things are some of the loops that we are rare to behave like other way.) \textbf{What am I discarding?} To get rid of my load and move on. But for what? and also ought to be like that? (throw away them to same bin. (Some of people do not care too much bin and throw them whenever it is possible.)) Even if I discard some stuff I think that I am ignoring its potential and losing it. At that times I become very sad and feel very comfortable. I must have find to another place for it more suitable than a waste bin. At least I can give them someone else who can use it for own purposes. Do I really luxury of discard?

%Significance of thinking outside of the box (about trash) is actually breaking the loops. You have to look at differently from common perception. \textbf{Break the rules, break the loops} to realize the alternative. \comment{Even if the market gives many alternatives of commodities, why do people still seek the alternative? Is not is enough? What type of gap that industrial products can not fill the gaps. Neden tüm insanlara hitap etmiyor?}

%[Making exploration.] One of the encouraging factor is to work on trash is to find (or explore) something different from someone else's discard. Because it is ignored by discarding and therefore undiscovered. Wait us to be discovered. and possiblely (as picasso mentioned) discovered again and again. \comment{Different people from different culture bring new interperation, but it is exist all of things.}

%It contains evraka moments.

%[Motivation.] I can not throw them away. When I throw them I became sad for them. I have to find something useful for it. (Failure of imagination, failure of making meaning) Even if I can not find it, I can pass it to another person who can make use of it for own purposes. There is a lot of effort to produce objects and it seems that all this efforts are wasted. What I mention is not related about ultimate productivity. It is more close to being thoughtful, and taking responsibility of tools, items and objects that we are using. Rather than throwing out, creating a way that all are have chance to live together is much more close to my perception.

% Önceki chapterlarda insanların kişisel olarak objelerde neler buldukları önemliydi. Ben de burada kendiminkini anlatacağım. Benim için yeni bir şeyler üretmek için birer kaynak.

% NEW PART [collecting] 
Collecting discarded objects has carried out through the efforts of mine and people around me. Lars Eighner's instructions helped me a lot when collecting objects. He writes that 
\begin{quote}
Eating safely from the Dumpsters involves three principles, using the senses and common sense to evaluate the condition of the found materials, knowing the Dumpsters of a given area and checking them regularly, and seeking always to answer the question \singlequotes{Why was this discarded?} \citep[as cited in][6]{strasser1999waste}.
\end{quote}
I applied these instructions to my case and I checked some points regularly and seek the reason of why was it discarded. Details will be given later for each objects.

% ilk toplama hareketim aslinda belli noktalari konrtol etmek. Ama bunlari kesfetmem gerekti. Bunlari ise normal hayatin akisi icinde kesfettim.

% found photosdaki adam da boyle bir mod var acikcasi.

% nicin atildigina gelince. Fazlalim olmasi, isini bitirmis olmasi. Labda unutulanlar ozellikle fazlalik hatali olmasi. Ve kimsenin umursamadigi bir sey olmasi.

% copten beslenmek ile aslinda oldukca benzer noktalar var. Secerken konrol ediyorsun. Birakilma swbebini dusununce aslinda benim kulamnimjm icin uygun olmadigini anlayacaktim.

% Bozulduğu için mi yoksa şekli standartlara uygun düşmediği için mi atılmış agnes varda da gösterildiği gibi.

% [Mode of search] looking for waste bins. asking for people. realizing during the daily life. for example bank splits.
% ofis, varuna, bilkent labı gibi mekanlar aslında önemli. benim malzemelerin büyük kısmını bulduğum yerler. iş bankası mesela. found photos.

Moreover there are other rules that define the frame of collecting act. Paper or package must be trash or will be trashed. For this project anything must not intentionally bought to use as trash. In other words first rule is to consume less and generate less trash. Lots of trash is accessible. Aim is to reach them.

% ben kendim ve cevremdekilere bu is icin gereksiz yere cop urettirmemeliydim. Bu ise hile karistirmam olurdu.

%[owner of disard]
\quotes{The question of who owns these discards is not trivial} \cite{zimring2012encyclopedia}. This question makes me uncomfortable because of feeling that stealing that someone elses' objects. Particularly I felt it when collecting leaved out papers from Bilkent Computer Laboratory.

% birakilmis bir seyi alirken yasanan huzursuzluk olarak tanimlasak bunu daha uygun olabilir. Onun baskasina bir sekilde ait oldugunu biliyorsun.

% tolanilan mrkanlar ise onemli. Fakir mahallesinde toplamak ile, zengin mallallesinde toplamak ayni sey degil. Ve devldtin coplugunu karistirmak ayni sey degil. Cope bir seyin izi ki ondan kurtulmak icin oguticuler var. Mesela herkesinkagidini alamadim. Her seyinde kagidinialamdim. Bohle bir sey mumkun degil.

% http://newsroom.ucla.edu/stories/studying-trash-as-art-249200
%Trash is also regarded differently, depending on where you live. Last year, an undergrad in Zubiaurre’s honors collegium seminar went to a poor neighborhood and scavenged through people’s trash; no one cared, Zubiaurre said. But when the same student went to Beverly Hills to go through trash, the police were nearly called. “Who decides what is public and what is private? How come trash becomes highly private in a rich neighborhood, but truly disposable in a poor neighborhood?” Zubiaurre said.

% bırakıldığını nasıl anlıyordum vs. Uzun sure bekleyince. Zaten bunlarda cope gidiyorlar. Temizlikcinin onlari topladigini gordum ne de olsa ben.

%[people]
% Bu kısmın daha güzel anlatılması gerekli.
% TODO ref.
As mentioned previously many people contributed to the project by collecting. Whenever i meet my friends I ask them to save their discard. The importance of collaboration with them can be understood the term "citizen science" which is \quotes{defined as scientific research performed in part or in whole by volunteers who are not professional scientists} \citep{robson2012using}. I need to note that this is not a scientific project but the notion belongs there. The value of it lies in the collective intelligence of the contributors. In the scope of this thesis the term can be interpreted as people bring their own creativity and interpretation to the project by collecting the items that they reach and select. When the number of contributors are increased the diversity of the collected material will be increased and this will echoed in the notebooks.

It can be viewed as a co-authored work. Because many people helped me to collect the papers and also many people leave their trail to the paper and also they bring meaning to the them. After production of papers I also want them to continue as co-authored process. In other words many people will be part of this project. As people see different things on objects and bring them to me. the variety of things is increased in time. Because people sad me that \quotes{I thought that you can use it. Do you collect also these?}.

% ayni zamanda baska insanlarin da yaraticiligi bu is. Bilkente gidip o kagitlari almaliyim ben.

% They provide me the materials to transform it. They select the items and find them. They bring their approach and selection. They are part of the selection of the materials. They started to engage with the work. People bring the material also wonder the result of it.

@@

%[disposable paper, packaging]
Collected items are mainly disposables ones. Most of them are paper or contains paper pulp. The word paper comes from papyrus, the plant that was first used for writing in ancient Egypt long before the making of paper in China. It is fundamental medium for writing, reading, education, communication, information storage and many others. Its role in the development of human civilization can not be neglected. (Paper in several forms is consumed on a daily basis \cite{trafford2012paper}.) Wide range of use from packing to newspaper makes it indispensable product for people. On the other hand for artist it offers great diversity in order to make compositions as can be seen in the works of collage. Further it is easy to find and collect them. Even if it is thrown out, still appropriate for painting and writing.

% TODO: Free ve accessible olması experiment yapmak için önemli bir yere getiriyor onu.

@@

% meaning of paper for me

% kagit benim cevremde cok fazla kullanilan bir sey.

% [Why do I collect trash?] Herkes neye ihtiyacı var ise onu toplar. Ben neden niçin topluyorum? Toplama sebepleri? Dönüştürme sebepleri. Neden sadece toplamakla yetinmiyorum. yani toplamak ile ayrıldığı noktalar nelerdir. Ben bir mana mı arıyorum? Yoksa kaybetmekten mi korkuyorum? Yeni kompozisyonlar oluşturmak istiyorum. Farklı karşımlar elde etmek istiyorum. Bir tür şaşırtmak durumu... Beklenmeyeni yapmak... En olmadık malzeme çöple çalışmak bu yüzden önemli benim için.

Collected items are stored in my room. All of they are varies. Most of them are not belong to me. Here the detailed information of the collected materials are listed.

\begin{figure}[h!]
  \centering
  \includegraphics[height=10cm]{project_graphics/collected_all_together.jpg}
  \caption{Collected materials}
  \label{fig:CollectedAllTogether}
\end{figure}

@@

% Bir kısmı çalıştığım ofiste tüketilen kahve paketlerinin ve onların taşındıkları poşetlerden oluşmakta. Diğerleri arkadaşın ofisinden, bir kısmı hocamdan. Bir kısmı da benim yoldan topladıklarım.

@@

% Elimde bazılarının fotoğrafları var bazılarının ise yok.

@@

@@

@@

@@

% websitesinde amac bun!ari anlatabilmekti.

@@

@@

% TODO sabahleyin bir fotoğrafını çek bunların.

@@

@@

Moreover I have reviewed other notebook projects. Notable ones are The Sketchbook Project and myDetour from Moleskine. In these projects anyone who bought the notebooks from them can participate and send their notebooks filled with illustrations and paintings. These projects can be seen as crowd-sourced library. Further the pages of the notebooks are available at online. After checking sketches in these notebooks, the diversity of them surprised me a lot. It forced me think that the transformation process is not limited with the production of notebooks from trash. After notebooks are given to the people, their transformation will continue. Therefore I think the process of transformation is a continuous act.
% amaç çeşitliliği arttırmak olduğu için

% TODO siteye nasıl karar verdin la?

>>>>

% The chapter that follows is divided into three sections

@@

%
%
% TODO: Be careful on tenses.
\section{The Statement}
% --disgusting, abject, unattractive, harmful to the people and nature--
Refuse is part of people’s consumption practices. It is a very common concept from developed cities to rural areas, from modern societies to ancient societies. It is not wanted, thrown away, kept away. It is considered as useless and disgusting. Contrary to the common approach as \cite{thompson1979rubbish}, author of the book Rubbish Theory, stated \quotes{one man's trash is another man's treasure}.

% people are invited in the phase of collecting and finding trash that is every where and produced every time.
With the collaboration of many people discarded papers and packages were collected from different places. This time, it was not thrown away, it was collected and saved. Later they were transformed to notebooks by hand with traditional methods. Juxtaposition of trashes create notebooks that are different from the blank industrial ones, and through them challenged the widespread understanding of trash.

@@

% This project aims to find new potentials on trash. This project asks people to readmit the trash to the their life.

@@

% Artist's work and their approach supported my project.
Through the process, there are several problems that needed to be solved. Some of the questions in my mind are solved through the research on trash. Further, the found samples of artworks helped me a lot to shape unclear points of the project. They provide me a deeper understanding of the subject and what I am doing. They lead me during the development of the work.
% played significant role, solved problems.
% It is evolved in time and affected from other artists' work, and gain meaning from research.

% This progress also reveals that how this work can be positioned among the other works.

@@

% [Song Dong]
The main idea is to save them to use later. For some people it is a life saving practice. It can be seen in the case of artist Song Dong's mother (mentioned in chapter 2). This practice result in establishing stronger (intimate) relationship with objects.

% TODO artist name

I am very uncomfortable with the act of discarding. I often think that by discarding objects, I am missing their potentials. I must find another use which is more effective than throwing away. At least I can give them to someone else who can use it for own purposes. As artist X argues that it is a "failure of imagination". There is a lot of effort to produce objects and it seems that all this efforts are wasted. What I mention is not related about ultimate productivity. It is more close to being thoughtful, and taking responsibility of tools, items and objects that we are using. Rather than throwing out, creating a way that all are have chance to live together is much more close to my perception. On the contrary, sometimes I became overwhelmed because of the significant amount of leftover from daily activities and in order to move on I need to leave them behind. It is the result of inevitable rhythm of modern life style. Consuming and wasting is part of people's daily routine and most of the time they are not aware of what they consume, and what they discard. In the scope of this thesis subject, saving objects rather them getting rid of them is an effective way of breaking the routines. The use of that object can be decided in the future.

% [encouraging point]
One of the encouraging factor of working on trash is to explore something different that others cannot see. In other words, it contains eureka moments. Because it is ignored by discarding and therefore undiscovered. Wait us to be discovered and possibly (as Picasso explanation on his work 'Bull's Head') discovered again and again.

% [EXPERIMENTS AT HOME]
My remarkable interaction with trash is from recent years. Long years I stayed at dormitory during when I was high school and university while undergraduate. Dormitory is place that living spaces is shared with many people. Therefore there is a limited place for you and your possessions. There is no space for unused items. After I graduated from university I started to living a rented house. This give me to opportunity to save the materials to use them later. My very first intention is to use them on my painting. Instead of white blank canvas I want to experiment with different surfaces. I collected boxes and cart boards from my friends. My aim is to turn discard materials to the different things. Here is some of the my previous works.

@@

% TODO Free material add reference here.
My purpose in these work is to paint on different surfaces, experiment new materials. They are not flat, not blank. These surfaces bring their previous histories to the painting. Another factor is they are free and easily available. Therefore I can make many experiments on these materials. After I completed them, I showed them people around me and give them as a gift.

@@

% But covering things are not new actually, when we were studying at primary school, we covered our books and notebooks. My mother, she is also a teacher, still covers her books things whatever at hand. (I have remembered that we are covering our notebooks at school. Sometimes we also cover the books.)

% TODO referans hatası olabilir.
% NEW PART [collecting] 
Collecting discarded objects has carried out through the efforts of mine and people around me. Lars Eighner's instructions helped me a lot when collecting objects. He writes that 
\begin{quote}
Eating safely from the Dumpsters involves three principles, using the senses and common sense to evaluate the condition of the found materials, knowing the Dumpsters of a given area and checking them regularly, and seeking always to answer the question \singlequotes{Why was this discarded?} \citep[as cited in][6]{strasser1999waste}.
\end{quote}
I applied these instructions to my case and I checked some points regularly and seek the reason of why was it discarded. Details will be given later for each objects.

% There are similar points with my practice. I also check the condition of material.

% TODO Sanatçı adını bulmak gerekli.
% It can be viewed as mode of search for objects and it can be seen clearly on Dick Jewlss found photos.

% Firstly I need to explore different locations to collect items. Most of them are not obvious for me. I discovered them on the flow of normal life and tasks.

% The reason of why they are leaved behind is not obvious but technical errors, printing wrong versions and extra copies can be easily guessed after a little observation. Nobody cares others print out.

% The need to the item is ended up and it is least profitable to save it. Now it is considered as excess.

% Does it discarded because of rotten, not fitting industrial standard or being surplus (production excess)? For instance, in the documentary film of Agnés Varda, she records the potatoes that are discarded because of not fitting the industrial standards. Therefore these potatoes fall into the category of edible (eatable). They are in good quality but not liked shape???

% [Mode of search] looking for waste bins. asking for people. realizing during the daily life. for example bank splits. I discover them during my life. For instance,  after I leaved bank split I realized that I can use them in my notebooks. Back of the splits are empty and appropriate for writing. Lots of them are used in the bank. The other places are discovered while daily life continues.

Moreover there are other rules that define the frame of collecting act. Paper or package must be trash or will be trashed. For this project anything must not intentionally bought to use as trash. In other words first rule is to consume less and generate less trash. Lots of trash is already produced every time everywhere. Aim is to reach them.

% OWNER
\quotes{The question of who owns these discards is not trivial} \cite{zimring2012encyclopedia}. This question makes me feel uncomfortable because of thinking that stealing that someone elses' objects. Particularly I felt it when collecting leaved out papers from Bilkent Computer Laboratory. You already know that it owned by somebody else and after a while owner can take them. I solved this issue checking the leaved papers in every couples hours. If it stays there I take them. Further I encountered that If nobody takes them for a long time servants collect them.

% TODO reference gerekli.
% http://newsroom.ucla.edu/stories/studying-trash-as-art-249200
The issue of owner becomes more complicated when owners' social status considered. Zubiaurre mentions that no body cares her student scavenged through people’s trash in a poor neighborhood. On the contrary when the same student went to Beverly Hills home of the many actors and celebrities in California to scavenge nearly the police were called.

% CONTRIBUTIONS OF PEOPLE
% Bu kısmın daha güzel anlatılması gerekli.
% TODO ref.
As mentioned previously many people contributed to the project by collecting. Whenever i meet my friends I ask them to save their discard. The importance of collaboration with them can be understood the term "citizen science" which is \quotes{defined as scientific research performed in part or in whole by volunteers who are not professional scientists} \citep{robson2012using}. I need to note that this is not a scientific project but the notion belongs there. The value of it lies in the collective intelligence of the contributors. In the scope of this thesis the term can be interpreted as people bring their own creativity and interpretation to the project by collecting the items that they reach and select. When the number of contributors are increased the diversity of the collected material will be increased and this will echoed in the notebooks.

It can be viewed as a co-authored work. Because many people helped me to collect the papers and also many people leave their trail to the paper and also they bring meaning to the them. After production of papers I also want them to continue as co-authored process. In other words many people will be part of this project. As people see different things on objects and bring them to me. the variety of things is increased in time. Because people sad me that \quotes{I thought that you can use it. Do you collect also these?}. They bring their unique approach.

% They provide me the materials to transform it. They select the items and find them. They bring their approach and selection. They are part of the selection of the materials. They started to engage with the work. People bring the material also wonder the result of it. Further people see me when collecting objects and transporting them wonders their purpose.

@@

%[disposable paper, packaging]
Collected items are mainly disposables ones. Most of them are paper or made from paper. The word paper comes from papyrus, the plant that was first used for writing in ancient Egypt long before the making of paper in China. In modern times all types and qualities of paper such as newspaper paper, print paper, and carton used for boxes pass through the same basic method of manufacture \citep{trafford2012paper}. It is fundamental medium for writing, reading, education, communication, information storage and many others. Its role in the development of human civilization can not be neglected. (Paper in several forms is consumed on a daily basis \cite{trafford2012paper}.) Wide range of use from packing to newspaper makes it indispensable product for people. On the other hand for artist it offers great diversity in order to make compositions as can be seen in the works of collage. Further it is easy to find and collect them. Even if it is thrown out, still appropriate for painting and writing.

@@

% [importance of paper for me]
% ilki resimden geliyor. Onu toplamaya başladım. ve daha onu tükettiğimi düşünmüyorum. bana hala bir sürü imkan tanıdığını düşünüyorum. Bir de yaygın kullanılması. Hala daha kimsenin görmediği küçük noktaları görmeye başlamamış olabilir.

% The importance of paper cames from previoulsy I mentioned.

% Not only important for the community but also for me.

% Kagit benim cevremde cok fazla kullanilan bir sey. yaygın kullanımı olması.

% Çok basit bir şekilde çöp olarak görülen bir şeyi başka bir şey olarak görmek keyifli bir şey benim için. zaten dönüştürmek kullanmak için topluyorum.

% Dönüştürme sebepleri. Neden sadece toplamakla yetinmiyorum. Yeni kompozisyonlar oluşturmak istiyorum. Farklı karşımlar elde etmek istiyorum. Bir tür şaşırtmak durumu... Beklenmeyeni yapmak... En olmadık malzeme çöple çalışmak bu yüzden önemli benim için.

Collected items are stored in my room for a long time. Most of them are not belong to me. Here the detailed information of the collected materials including the place where it is collected and their usage are listed.

% Bu resme gerek olmayabilir. Appendixe konulabilir.
\begin{figure}[h!]
  \centering
  \includegraphics[height=10cm]{project_graphics/collected_all_together.jpg}
  \caption{Collected materials}
  \label{fig:CollectedAllTogether}
\end{figure}

@@

% Bir kısmı çalıştığım ofiste tüketilen kahve paketlerinin ve onların taşındıkları poşetlerden oluşmakta. Diğerleri arkadaşın ofisinden, bir kısmı ise hocamdan. Bir kısmı da benim yoldan topladıklarım.

@@

% Elimde bazılarının fotoğrafları var bazılarının ise yok. Yani bazılarının kayıtları var, bazılarının ise yok.

@@

% Nothing is inherently trash(5). matter out of place. Dirt is relative emphasize. "Shoes are not dirty in themselves, but it is dirty to place them on the dining table; food is not dirty in itself but it is dirty to leave cooking utensils in the bedroom, or food bespattered on clothing; similarly bathroom equipment in the drawing room; clothing lying on chairs; out-door things in-doors; upstairs things downstairs; under-clothing appearing where over-clothing should be and so on" (Douglas 2003, 36-7)

@@

% Buradaki kağıtlar tüm yemek masasının üzerine örtüyor. büyük bir rulo halinde masanın başında bulunuyor. yemek yendikten sonra masanın üzerindeki kısım yırtılıp atılıyor. yenisi rulodan seriliyor. ne kadar kağıt harcandığı bir bakışta anlaşılmakta. Tüm o rulodaki kağıtlar çöpe gidecek. Arkadaşlarla bir gün dışarı gittikten sonra buradaki kağıtları farkettim ve çıkışta onlar eskileri toplarken kağıtları topladım.

@@

% arkadaşlarla yemeğe gittikten sonra kasiyerdeki arkaştan defterleri burada verip veremeyeceğimi sorduktan sonra bana ellerindeki kağıtlardan bahsetti ve onları verebileceğinden bahsetti.

@@

% websitesinde amac bunlari anlatabilmekti.

@@

% özellikle içinde kullandığım kağıtları karıştırarak oluşturdum. Burda dada şiiri ile benzerlikler içermekte.

@@

@@

% Defter dikme yöntemi ???

% Kullandığım malzemeler. İğne, iplik, makas, maket bıçağı, raptiye, yapıştırıcı, ve yapıştırıcı.

@@

Moreover I have reviewed other notebook projects. Notable ones are The Sketchbook Project and myDetour from Moleskine. In these projects anyone who bought the notebooks from them can participate and send their notebooks filled with illustrations and paintings. These projects can be seen as crowd-sourced library. Further the pages of the notebooks are available at online. After checking sketches in these notebooks, the diversity of them surprised me a lot. It forced me think that the transformation process is not limited with the production of notebooks from trash. After notebooks are given to the people, their transformation will continue. Therefore I think the process of transformation is a continuous act.

% amaç çeşitliliği arttırmak

### 2016-01-01 chapter5.tex
updates
Former-commit-id: ed8c3a549dfd42e9a1714a8835097ccd033fd632

Trash is everywhere. Part of our activities. Rubbish as an object state is not static. Its value, usage may vary according to the people. Artistic intentions are aimed to transform the material. Whatever the reason that people are discarding things there must be other type of action that can be able to reverse it. Aimed to create new possibilities from trash.

@@

Their methodologies are different. Their works can be viewed in various dimensions. Their works are also show that the great diversity and the potential usages of trash. 
There are different motivations.

@@

%
%
\textbf{Evolution, Critics} During the process I have also generated lots of trashed papers. Cutting and pasting things also leave unused items. I do not know what to do with them. It is hard to use all of them. Saved for later use. On the other hand being aware of this trasnformation act is very tiny part of the big picture. I can say that my trash is reduced but is it same for the other people. Hard to collect all of them.

There is also discard is being generated during the production process of papers. How to use them? Need to find a way because varda uses her discarded item inside of the film. Always(or in every proceses) new discard items are generated.

@@

% Buradaki en önemli amaç değiştirmek dönüştürmek, sadece çöpü dönüştürmek yetmez, insanların fikirlerini de dönüştürmek gerekli ve bu bir süreç işi.

>>>>

Inseparable part of our activities.
Trash is everywhere. Part of our activities. Rubbish as an object state is not static. Its value, usage may vary according to the people. Artistic intentions are aimed to transform the material. Whatever the reason that people are discarding things there must be other type of action that can be able to reverse it. Aimed to create new possibilities from trash.

% This thesis forms the basic principles and approaches in the act of transformation. This research provides a framework to look at trash differently.

% This thesis work attempts to understand the transformation of trash through the artistic practices. The usage of materials in these works provide audience new interpretation of the material.

% Through the analysis of selected works metadologies, approaches, placement trash, positing of trash ...  show that trash is fluid, and value indeterminate, and are often determined by context and personal subjectivities.

% Our evaluations of what is 'rubbish' and 'art' or 'useful/non-useful' and 'good/bad' is both content and context dependent and are not fixed values. Apparent polar opposites of 'rubbish' and 'art' are blurred notions that are explored in many art works using rubbish materials. Indeed, temporal value judgements of 'rubbish' and 'art' are often at the core of such art works.

% This research began through a desire to understand more about the subject of rubbish in art practice. (or especially turning discarded papers to notebooks from a hobby to framed project or research.)

% While the notebooks have potentials to be rubbish, records of them in the website are preserved.

% In the project notebooks are given away. They are transformed to trash and served to the flow again. They will continue to flow. There is a possibility that they can be trashed again. However vice verse is possible. In other words has potential be turn to durable. Decision belongs to people again.

% Through this research another dimension of trash is explored. This present more solid understanding of trash.

% Sanatçıların sorguladıkları şeylerin sonuçlarını görmek gerekli. Neden çöpü kullanıyorlar. İlkinde  geleneksel yöntemleri terk etmeleri,

% This research present different uses of trash and approaches. This suggests that it provides to artists wide range of representation styles. (limitless possibilities)

% In the introduction part, questioned the why artist choose to use discarded material. examples, different approaches. what are they.

% But it cannot be completely explained by trend of moving away from traditional methods, modern times throwaway spirit play significant role in this movement.

@@

Their methodologies are different. Their works can be viewed in various dimensions. Their works are also show that the great diversity and the potential usages of trash. There are different motivations. (Artist have different motivations and interpretations on trash.)

@@

%
%
\textbf{Evolution, Critics} During the process I have also generated lots of trashed papers. Cutting and pasting things also leave unused items. I do not know what to do with them. It is hard to use all of them. Saved for later use. On the other hand being aware of this transformation act is very tiny part of the big picture. I can say that my trash is reduced but is it same for the other people. Hard to collect all of them. 
There is also discard is being generated during the production process of papers. How to use them? Need to find a way because varda uses her discarded item inside of the film. Always(or in every processes) new discard items are generated.

@@

% The purpose is here to find new possibilities and dimensions to see the objects. The physically transforming objects is not sufficient, at the same time it will change people's viewpoint.

% try to the capture the reality behind the consumption practices.

% transform to their daily trash, use them for their on artist purposes, surface for their art.

% how it is essential for some people.

% as a portrait of them.

% zim car,

% Duchamp, beyond the objects, the ideas embeded them gain importance when considering artworks.

% many possibilities in terms of their shape, size and color. offer great diversity.

% narratives through the people's discard. the image of people, their

% record of their trash, preserving the images of them, or the others.

% destructive manner, break down

% form - structure - shape

% different forms of trash. modes, practices, type, kind.

% photos, everyday objects, disposables, luxury possessions like car.

% place of trash

% different people touches on trash. different cultures, different manner

% for us and artist it is a source of diversity. for their work, representation and expression.

% it is not only found in landfill but also can be found in museums.

- çöpün değişik formları. çöpü kullanmanın değişik formları. çöpün hayattaki değişik formları.
- çöpe dokunan farklı insanlar.
- o yüzden bizim için bir çeşitliliğin kaynağı
- o yüzden kaynak.
- o yüzden hazine
- nasıl bir hazine, ifade aracı olarak birer hazine.
- sadece çöplüklerde değil aynı zamanda müzelerde,

% The initial reduction of the research scope leaves potentially much more relevant work to be done. Certain major avenues have not been discussed in depth, not because they are irrelevant, but because there simply has not been time or space to explore them in sufficient detail and some reduction in scope has been necessary to be specific in such a wide field

% For example, virtual/digital rubbish-as-art was specifically omitted in this project due to the object/material-basis of the enquiry. However, through the project development, the informal language basis of exchange in understanding the value of rubbish-as-art has proven fundamental and a further area to develop, which will most likely include in the virtual/digital realm. The question of whether there still needs to be a material/object basis of this further investigation is yet to be answered.

% The focus on material waste in art in this study has also largely omitted waste of other non-material things such as time. Wasting time as art and the relationship to labour and value is another significant area of exploration. The relationship between wasting time and material waste as documentation that is evident in some studied art works has not been developed in this thesis. Again, there is much potential for further work in this area and also links in with notions of value of online exchange also as 'wasting time'.

% Future works, as mentioned the value and meaning objects changes people to people society to society. Therefore more focused research can be conducted to analyze the local practices of transformation. the history and the place of the peoples life.

% Different selection of works and their analysis and relation between them will form another thesis which identifies another dimension of trash.

% Paraphrase 
%This thesis takes a rather different approach to the discarded objects. It looks to philosophical ideas and our entangled experiences of things, time and stories, which need to be traversed in order for a discarded object to be called ‘waste’.
